An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-12-06 tex/paper.tex
Pointing at label.
Adding to section about reproducing tournaments.
Have code.
Could possibly be nice to include example/details about how far we are
from Axelrod's first tournament.

This just shows the very basic utilisation of the library and further details
can be found at the online documentation:
\url{http://axelrod.readthedocs.org}. Some further implemented capabilities include:

@@

Stewart and Plotkin 2012 is fully reproducible; results are unstable (e.g.\
substituting \texttt{soft\_majo} for \texttt{hard\_majo} changes the results).

>>>>

Figure \ref{fig:demo_tournament_commands} just shows the very basic utilisation
of the library and further details can be found at the online documentation:
\url{http://axelrod.readthedocs.org}. Some further implemented capabilities
include:

@@

Due to the open nature of the library the number of strategies included has
grown at a fast pace, as can be seen in
Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
previous research being done in an irreproducible way due to, for example no
source code, and/or vaguely described strategies; not all previous tournaments
are yet to be reproduced.

\begin{figure}[!hbtp] \centering
    \includegraphics[width=.8\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
    \caption{The number of strategies included in the library}
    \label{fig:number_of_strategies_against_date}
\end{figure}

One tournament that is possible to reproduce is that of
\cite{Stewart2012}. The strategies used in that tournament are the following:

\begin{enumerate}
    \item Cooperator
    \item Defector
    \item ZD-Extort-2
    \item Joss: 0.9
    \item Hard Tit For Tat
    \item Hard Tit For 2 Tats
    \item Tit For Tat
    \item Grudger
    \item Tit For 2 Tats
    \item Win-Stay Lose-Shift
    \item Random: 0.5
    \item ZD-GTFT-2
    \item GTFT: 0.33
    \item Hard Prober
    \item Prober
    \item Prober 2
    \item Prober 3
    \item Calculator
    \item Hard Go By Majority
\end{enumerate}

This can be reproduced as shown in Figure~\ref{fig:stewart-code}, which gives
the plot of Figure~\ref{fig:stewart_tournament}.

\begin{figure}[!hbtp]
    \begin{minted}[breaklines, linenos, frame=lines]{python}
>>> import axelrod

>>> strategies = [axelrod.Cooperator(),
....              axelrod.Defector(),
....              axelrod.ZDExtort2(),
....              axelrod.Joss(),
....              axelrod.HardTitForTat(),
....              axelrod.HardTitFor2Tats(),
....              axelrod.TitForTat(),
....              axelrod.Grudger(),
....              axelrod.TitFor2Tats(),
....              axelrod.WinStayLoseShift(),
....              axelrod.Random(),
....              axelrod.ZDGTFT2(),
....              axelrod.GTFT(),
....              axelrod.HardProber(),
....              axelrod.Prober(),
....              axelrod.Prober2(),
....              axelrod.Prober3(),
....              axelrod.Calculator(),
....              axelrod.HardGoByMajority()]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> p = plot.boxplot()
    \end{minted}
    \caption{Source code for the Grudger strategy.}
    \label{fig:stewart-code}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/stewart_tournament.pdf}
    \caption{The results from a simple tournament.}
    \label{fig:stewart_tournament}
\end{figure}

Work is actively ongoing to include more strategies. In the next Section, an
overview of some of the early and novel research insights made possible by the
library.
